A Study on Common Bug Fix Patterns in Rust

### 2022-11-03 discussion.tex
changes to be made

Furthermore, we expected to obtain certain patterns regarding some certain Rust related features, such as unsafe Rust, but our results did not include those patterns. Our speculation is that, since Rust has a strong compiler check before creating the program executable, the programmers usually get many errors, and they only push their code once it is free of compile errors. That is why, we think there are some patterns that were hidden from our sight.

>>>>

Furthermore, we expected to obtain certain patterns regarding some certain Rust related features, such as \verb+move+, but our results did not include those patterns. Our speculation is that, since Rust has a strong compiler check before creating the program executable, the programmers usually get many errors, and they only push their code once it is free of compile errors. That is why, we think there are some patterns that were hidden from our sight.

### 2022-11-03 results.tex
changes to be made

\todo[inline]{Can we justify the 50, both here and in the previous section? ``It was a random number not so large and not too small, how can I justify it?''}

@@

\todo[inline]{no, you have to compute the intersection. ``The numbers reported are the intersection'' when is our approach effective and when is it not? ``added above'' more detailed stats would probably be good too ``what kind of stats do you have in mind?''}

@@

\begin{tabular}{l|l|r|r}
\textbf{Catgegory} & \textbf{ID} & \textbf{\# Instances} & \textbf{\# Projects} \\
\hline
\multirow{2}{*}{Attributes} & G.attr.struct & 172 & 16                                  \\
& G.attr.struct.field & 62 & 16                     \\\cline{1-4}
\multirow{2}{*}{Struct} & G.struct.field  & 179 & 17\\
& G.struct.field.pub & 23 & 12   
\\\cline{1-4}
Option & G.option & 22 & 12                    \\\cline{1-4}
\multirow{4}{*}{Types} & G.type.field  & 72 & 14 \\
& G.type.generic & 46 & 14\\ & G.type.enum.variant  & 39 & 12 \\
& G.type.tuple & 6 & 6                                         \\\cline{1-4}
\multirow{1}{*}{Traits} & G.trait.bound & 6 & 5 \\\cline{1-4}
\multirow{2}{*}{Match} & G.match.pattern & 41 & 12 \\
& G.match.code & 8 & 5 \\
\end{tabular}
\caption{\label{table:general}Bug Fix Pattern Categorization (General Patterns)}
\end{table}
\todo[inline]{Also do we compare table 2 to what occurs in previous work? ``What previous work?''}

@@

\todo[inline]{I think you should talk more about ``does not modify program behaviour''. For instance after you make this change the program may no longer compile. Is it true that, if it compiles, behaviour is preserved? ``Yes the assumption is that if the presence of clone() is unnecessary, then removing it would not change the program behaviour''}

>>>>

\todo[inline]{Can we justify the 50, both here and in the previous section? ``It was a random number not so large and not too small, how can I justify it?'' Ask about calculating error, give yourself more credit for 50 before}

@@

\todo[inline]{no, you have to compute the intersection. ``The numbers reported are the intersection'' when is our approach effective and when is it not? ``added above'' more detailed stats would probably be good too ``what kind of stats do you have in mind?'' add a table for describing why it didn't work}

@@

\begin{tabular}{l|l|r|r}
\textbf{Catgegory} & \textbf{ID} & \textbf{\# Instances} & \textbf{\# Projects} \\
\hline
\multirow{2}{*}{Attributes} & G.attr.struct & 172 & 16                                  \\
& G.attr.struct.field & 62 & 16                     \\\cline{1-4}
\multirow{2}{*}{Struct} & G.struct.field  & 179 & 17\\
& G.struct.field.pub & 23 & 12   
\\\cline{1-4}
Option & G.option & 22 & 12                    \\\cline{1-4}
\multirow{4}{*}{Types} & G.type.field  & 72 & 14 \\
& G.type.generic & 46 & 14\\ & G.type.enum.variant  & 39 & 12 \\
& G.type.tuple & 6 & 6                                         \\\cline{1-4}
\multirow{1}{*}{Traits} & G.trait.bound & 6 & 5 \\\cline{1-4}
\multirow{2}{*}{Match} & G.match.pattern & 41 & 12 \\
& G.match.code & 8 & 5 \\
\end{tabular}
\caption{\label{table:general}Bug Fix Pattern Categorization (General Patterns)}
\end{table}
\todo[inline]{Also do we compare table 2 to what occurs in previous work? ``What previous work?'' add languages per desc}

@@

\todo[inline]{I think you should talk more about ``does not modify program behaviour''. For instance after you make this change the program may no longer compile. Is it true that, if it compiles, behaviour is preserved? ``Yes the assumption is that if the presence of clone() is unnecessary, then removing it would not change the program behaviour'' rephrase tautology}
